---
title: "Ufo_and_Beyond"
author: "Renzo"
date: "05/06/2021"
output: html_document
---

---
title: "UFO and_beyond"
output: html_notebook
---

# Reading data and formatting
```{r}
library(tidyverse)
library(data.table)
library(ggplot2)
library(lubridate)
library(maps)
library(mapdata)
```

```{r}
### Read CSV file

ufo<-read_csv("DATA/scrubbed.csv")
ufo$datetime <- mdy_hm(ufo$datetime) # Date format
ufo$`date posted` <- mdy(ufo$`date posted`)
ufo$`duration (seconds)` <- as.numeric(ufo$`duration (seconds)`)

ufo$country <- as.factor(ufo$country) # Format country
levels(ufo$country) <- c("NA","Australia","Canada","Germany","Great Britain","US")
```

```{r}
# Ufos by Country

ggplot(ufo,aes(country,fill=country))+
  stat_count()+ggtitle("UFOS by country")
```

# Ufos by shape
```{r}
ggplot(ufo,aes(shape,fill=shape))+
  stat_count()+ggtitle("UFOS by Shape")+theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 45, size=8,hjust = 1))
ufo[,.N,by=shape][order(-N)]
```

The most usual UFO shape is *light* and the number 4 is *fireball*, strictly they are Uknown Flying Objects, but if we are looking for aliens, a simple light or fireball is not a serious shape to deduct the existence of aliens. 
One thing that surprised me is that the most common *serious* shape is a triangle, rather than a circle 

# WorldMap UFOs
```{r}
ufo$latitude <- as.numeric(ufo$latitude)

map <- borders("world", colour="black", fill="gray50") 
ufo_map <- ggplot(ufo) + map 
print(ufo_map + geom_point(aes(x=ufo$longitude, y=ufo$latitude,color=shape),shape=18) +
        theme(legend.position = "top")+
        ggtitle("UFOs"))
```

These are mainly first world UFOs, usually they only visit the developed countries.


## Year
```{r, echo=FALSE}
ufo_year <- ufo[,.N,by=year][order(-year)]
ggplot(ufo_year[year>1940],aes(x = year,y = N,fill=N))+
  geom_bar(stat = "identity")+ggtitle("UFOs by year")
```

## Month
```{r, echo=FALSE}
ufo_month <- ufo[,.N,by=month]
ggplot(ufo_month,aes(x = month,y = N,fill=N))+
  geom_bar(stat = "identity")+ggtitle("UFOs by month")
```

# Wordcloud UFO comments{.tabset}

## Random Sample
```{r, echo=FALSE}
library('stringr')
library('readr')
library('wordcloud')
library('tm')
library('SnowballC')
library('RWeka')
library('RSentiment')
library(DT)
set.seed(100)
ufo_sample = sample(ufo$comments, 10000)
corpus = Corpus(VectorSource(list(ufo_sample)))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers) 
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords('english'))

dtm_ufo = DocumentTermMatrix(VCorpus(VectorSource(corpus[[1]]$content)))
freq_ufo <- colSums(as.matrix(dtm_ufo))
sentiments_ufo = calculate_sentiment(names(freq_ufo))
sentiments_ufo = cbind(sentiments_ufo, as.data.frame(freq_ufo))

wordcloud(words = sentiments_ufo$text,freq = sentiments_ufo$freq_ufo,max.words = 100, colors=brewer.pal(6,"Dark2"))
```

## Wordcloud in US
```{r, echo=FALSE}
ufo_sample = sample(ufo[country=="US",comments], 10000)
corpus = Corpus(VectorSource(list(ufo_sample)))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers) 
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords('english'))

dtm_ufo = DocumentTermMatrix(VCorpus(VectorSource(corpus[[1]]$content)))
freq_ufo <- colSums(as.matrix(dtm_ufo))
sentiments_ufo = calculate_sentiment(names(freq_ufo))
sentiments_ufo = cbind(sentiments_ufo, as.data.frame(freq_ufo))
wordcloud(words = sentiments_ufo$text,freq = sentiments_ufo$freq_ufo,max.words = 100, colors=brewer.pal(6,"Dark2"))
```


## Wordcloud in Great Britain
```{r, echo=FALSE}
corpus = Corpus(VectorSource(list(ufo[country=="Great Britain",comments])))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers) 
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords('english'))

dtm_ufo = DocumentTermMatrix(VCorpus(VectorSource(corpus[[1]]$content)))
freq_ufo <- colSums(as.matrix(dtm_ufo))
sentiments_ufo = calculate_sentiment(names(freq_ufo))
sentiments_ufo = cbind(sentiments_ufo, as.data.frame(freq_ufo))
wordcloud(words = sentiments_ufo$text,freq = sentiments_ufo$freq_ufo,max.words = 100, colors=brewer.pal(6,"Dark2"))
```

## Wordcloud in Germany
```{r, echo=FALSE}
corpus = Corpus(VectorSource(list(ufo[country=="Germany",comments])))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers) 
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords('english'))

dtm_ufo = DocumentTermMatrix(VCorpus(VectorSource(corpus[[1]]$content)))
freq_ufo <- colSums(as.matrix(dtm_ufo))
sentiments_ufo = calculate_sentiment(names(freq_ufo))
sentiments_ufo = cbind(sentiments_ufo, as.data.frame(freq_ufo))
wordcloud(words = sentiments_ufo$text,freq = sentiments_ufo$freq_ufo,max.words = 100, colors=brewer.pal(6,"Dark2"))
```

## Wordcloud in Canada
```{r, echo=FALSE}
corpus = Corpus(VectorSource(list(ufo[country=="Canada",comments])))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers) 
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords('english'))

dtm_ufo = DocumentTermMatrix(VCorpus(VectorSource(corpus[[1]]$content)))
freq_ufo <- colSums(as.matrix(dtm_ufo))
sentiments_ufo = calculate_sentiment(names(freq_ufo))
sentiments_ufo = cbind(sentiments_ufo, as.data.frame(freq_ufo))
wordcloud(words = sentiments_ufo$text,freq = sentiments_ufo$freq_ufo,max.words = 100, colors=brewer.pal(6,"Dark2"))
```

 
